### 2015-10-30 tex/proofs.tex
Brought in abstract, intro, and related work from CAV paper.
Removed apppendix and references. Fixed bib.

\section{Proofs}
\subsection{Lemmas}

@@

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^\prime^\rightarrow$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $p^+ \rightharpoonup_{h^\prime} q^+$.

>>>>

\section{Proofs}
\label{sec:proofs}
\subsection{Lemmas}

@@

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^{\prime^\rightarrow}$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $p^+ \rightharpoonup_{h^\prime} q^+$.

### 2015-10-30 vmcai-2016-tex/summary-heap.tex
Addressed reviewer concerns
Removed apppendix and references. Fixed bib.

The path condition is a predicate of the program variables. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation for update is used with $\cfgnt{L}$ and $\cfgnt{R}$ as well.

@@

\section{Operational Semantics}
This paper defines symbolic initialization using
a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
surface  syntax  (input) and machine  syntax (state) are shown
in~\figref{fig:syntax}. The machine syntax omits the list based syntactic structures for the partial functions in the heap etc.  Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

The rewrite relations for the more mundane portions of the language
that do not update the symbolic heap are in the appendix with more details in 
\cite{Hillery:2015}. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking. The
machine halts if no rewrite is enabled. In the rest of this paper the relation $s \rcom
s^\prime$ indicates that two states are related by these more
mundane rules.

>>>>

The path condition is a predicate of references in the heap. The environment is a partial function so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. This notation for update is used with $\cfgnt{L}$ and $\cfgnt{R}$ as well.

@@

\section{Operational Semantics}
This paper defines symbolic initialization using
a small-step operational semantics in the context of a syntactic machine with a CESK architecture~\cite{Felleisen:1992, saints-MS}. The
surface  syntax  (input) and machine  syntax (state) are shown
in~\figref{fig:syntax}. The machine syntax omits the list based syntactic structures for the partial functions in the heap etc.  Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness. The language only considers objects as values and does not support looping structures to focus the discussion on the symbolic heap representation.

@@

The rewrite relations for the more mundane portions of the language
that do not update the symbolic heap are in 
\cite{Hillery:2015}. Excepting \textrm{N{\footnotesize EW}}, the rules do not update
the heap, and are largely concerned with argument evaluation in an
expected way. It is assumed that only type safe programs are input to
the machine so there is no type checking. The
machine halts if no rewrite is enabled. In the rest of this paper the relation $s \rcom
s^\prime$ indicates that two states are related by these more
mundane rules.
